SDR enhancement by clouds

### 2024-03-23 article/article.Rmd
Commit 2024-03-23 21:12

The monitoring site is operating in the Laboratory of Atmospheric Physics of the
Aristotle University of Thessaloniki (\(40^\circ\,38'\,\)N,
\(22^\circ\,57'\,\)E, \(80\,\)m\ a.s.l.).
In this study we present data from the period
`r strftime(min(ST_daily$Date), "%d\\ %B %Y")` to
`r strftime(max(ST_daily$Date), "%d\\ %B %Y")`.
<!-- Instrument -->
The GHI data were measured with a Kipp\ & Zonen CM-21 pyranometer.  During the study
period, the pyranometer was independently calibrated three times at the
Meteorologisches Observatorium Lindenberg, DWD, verifying that the stability of the
instrument’s sensitivity was better than $0.7\%$ relative to the initial calibration
by the manufacturer.
<!-- Measurements -->
For the acquisition of radiometric data, the signal of the pyranometer was sampled at
a rate of $1\,\text{Hz}$.  The mean and the standard deviation of these samples were
calculated and recorded every minute.  The measurements were corrected for the zero
offset ("dark signal" in volts), which was calculated by averaging all measurements
recorded for a period of $3\,\text{h}$, before (morning) or after (evening) the Sun
reaches an elevation angle of $-10^\circ$.  The signal was converted to irradiance
using the ramped value of the instrument’s sensitivity between subsequent
calibrations.

<!-- Radiation data quality check -->
To further improve the quality of the irradiance data, a manual screening was
performed to remove inconsistent and erroneous recordings that can occur
stochastically or systematically during the continuous operation of the instruments.
The manual screening was aided by a radiation data quality assurance procedure,
adjusted for the site, which was based on the methods of Long and Shi\ [@Long2006;
@Long2008a].  Thus, problematic recordings have been excluded from further
processing.  Although it is impossible to detect all false data, the large number of
available data, and the aggregation scheme we used, ensures the quality of the
radiation measurements used in this study.
<!-- Data selection -->
To preserve an unbiased representation of the data we applied a constraint similar
the one used by @CastillejoCuberos2020. Where, for each valid hour of day, there
must exist at list 45 minutes of valid measurements, including nighttime near
sunrise and sunset. Days with less than 5 valid hours are rejected completely.
<!--# CastillejoCuberos2020 There must be at least 5 h of valid data (Tests 1–7),
otherwise all data for this day is flagged as invalid. There must be at least This
work valid data 45 min of valid data (Tests 1–7) for an hour to be flagged as valid,
otherwise all minute data for this hour is flagged as invalid. -->
Furthermore, due to the significant measurement uncertainty when the Sun is near the
horizon, and to some systematic obstructions by nearby buildings, we have excluded
all measurements with solar zenith angle (SZA) greater than $`r 90-BIO_ELEVA`^\circ$.

@@

To be able to detect the CE cases, we had establish a baseline, above which we can
characterize each data point as enhancement event, by estimating the occurring over
irradiance.  To have an estimation and a first insight on the phenomenon, we
experimented with two simple approaches as reference.  The Haurwitz's model
[@Haurwitz1945], which is as simple clear sky we have previous adjusted and had good
fit with our data [@Natsis2023], and the TSI at the top of the atmosphere.  For both
cases we tested using an appropriate relative threshold and/or an constant offset.
The initial results, showed that we can detect a big portion of the CE events. But it
was evident, by inspecting the daily plot of irradiance, that changes on the
atmospheric conditions introduced numerous false positive and false negative
results.  To produce a more accurate reference, we had to take into account more
factors that effect the clear sky radiation and used a radiation transfer model.

@@

We approximated the expected clear sky GHI by using a model.  Because of the lack of
observational data for the whole period, we used some long term climatological data
for the main factors responsible for the attenuation of the broadband downward solar
radiation in the atmosphere. Which are mainly the aerosols and the water vapors.
Fortunately, our site participates in the Aerosol Robotic Network (AERONET)
[@Giles2019; @Buis1998], as we operate a Cimel photometer since 2003, collocated with
the CM-21 pyranometer.  The mean monthly aerosol optical depth (AOD) on different
wavelengths is provided by AERONET, along with the equivalent water column height in
the atmosphere.  The simulation of the clear sky radiation was performed by the well
established radiation transfer model Libradtran [@Emde2016], a similar
approach, was also used by @Vamvakas2020.

@@

<!-- Lookup table -->
To create a look up table that aligns with our dataset we applied some adjustments.
To account for the Sun's variability in our one-minute GHI measurements, we corrected
the model's input spectrum integral to the one of the value of total solar irradiance
(TSI) provided by NOAA [@Coddington2005].  Also, we applied the effect of the Earth
-- Sun distance on the irradiance, by using the distance calculated by the Astropy
[@AstropyCollaboration2022] software library. As needed, we interpolate the
irradiances to the exact SZA of our measurements.  For each period of the year, we
used the appropriate atmospheric profile (afglms or afglmw).  Finally, we calculated
the clear sky irradiance value at the horizontal plane.  Thus, we were able to
emulate different atmospheric condition and level of atmospheric clearness for the
climatological conditions of the site.  Thus, the modeled clear sky irradiances,
based on the climatological conditions of the site, can be directly compared to each
measured one-minute value of GHI, for different conditions of atmospheric clearness.

@@

>>>>

The monitoring site is operating in the Laboratory of Atmospheric Physics of the
Aristotle University of Thessaloniki (\(40^\circ\,38'\,\)N,
\(22^\circ\,57'\,\)E, \(80\,\)m\ a.s.l.).
In this study we present data from the period
`r strftime(min(ST_daily$Date), "%d\\ %B %Y")` to
`r strftime(max(ST_daily$Date), "%d\\ %B %Y")`.
<!-- Instrument -->
The GHI data were measured with a Kipp\ & Zonen CM-21 pyranometer.  During the study
period, the pyranometer was independently calibrated three times at the
Meteorologisches Observatorium Lindenberg, DWD, verifying that the stability of the
instrument’s sensitivity was better than $0.7\%$ relative to the initial calibration
by the manufacturer.
<!-- Measurements -->
For the acquisition of radiometric data, the signal of the pyranometer was sampled at
a rate of $1\,\text{Hz}$.  The mean and the standard deviation of these samples were
calculated and recorded for every minute.  The measurements were corrected for the
zero offset ("dark signal" in volts), which was calculated by averaging all
measurements recorded for a period of $3\,\text{h}$, before (morning) or after
(evening) the Sun reaches an elevation angle of $-10^\circ$.  The signal was
converted to irradiance using the ramped value of the instrument’s sensitivity
between subsequent calibrations.

<!-- Radiation data quality check -->
To further improve the quality of the irradiance data, a manual screening was
performed to remove inconsistent and erroneous recordings that can occur
stochastically or systematically during the continuous operation of the instruments.
The manual screening was aided by a radiation data quality assurance procedure,
adjusted for the site, which was based on the methods of Long and Shi\ [@Long2006;
@Long2008a].  Thus, problematic recordings have been excluded from further
processing.  Although it is impossible to detect all false data, the large number of
available data, and the aggregation scheme we used, ensures the quality of the
radiation measurements used in this study.
<!-- Data selection -->
To preserve an unbiased representation of the data we applied a constraint, similar
the one used by @CastillejoCuberos2020. Where, for each valid hour of day, there must
exist at least 45 minutes of valid measurements, including nighttime near sunrise and
sunset. Days with less than 5 valid hours are rejected completely.
<!--# CastillejoCuberos2020 There must be at least 5 h of valid data (Tests 1–7),
otherwise all data for this day is flagged as invalid. There must be at least This
work valid data 45 min of valid data (Tests 1–7) for an hour to be flagged as valid,
otherwise all minute data for this hour is flagged as invalid. -->
Furthermore, due to the significant measurement uncertainty when the Sun is near the
horizon, and due to some systematic obstructions by nearby buildings, we have
excluded all measurements with solar zenith angle (SZA) greater than 
$`r 90 - BIO_ELEVA`^\circ$.

@@

To be able to detect the CE cases, we had to establish a baseline, above which we can
characterize each data point as an enhancement event, by estimating the occurring
over irradiance (OI).  To have an estimation and a first insight on the phenomenon,
we experimented with two simple approaches for the reference.  The Haurwitz's model
[@Haurwitz1945], which is as simple clear sky model, and we had already adjusted and
had good fit with our data [@Natsis2023], and the TSI at the top of the atmosphere.
We have tested both cases by using an appropriate relative threshold and/or an
additional constant offset.  The initial results, showed that we can detect a big
portion of the CE events. These results were helpful, and helped to establish some
criteria to further improve the CE identification. It was evident, by inspecting the
daily plot of irradiance, that changes on the atmospheric conditions introduced
numerous false positive and false negative results.  To produce a more accurate
reference, we had to take into account more factors that effect the clear sky
radiation. So we used a radiation transfer model.

@@

We approximated the expected clear sky GHI by using a model.  Because of the lack of
observational data for the whole period, we used some long term climatological data
for the main factors responsible for the attenuation of the broadband downward solar
radiation in the atmosphere. Which are mainly, the aerosols and the water vapors.
Fortunately, our site participates in the Aerosol Robotic Network (AERONET)
[@Giles2019; @Buis1998], as we operate a Cimel photometer since 2003, collocated with
the CM-21 pyranometer.  The mean monthly aerosol optical depth (AOD) on different
wavelengths is provided by AERONET, along with the equivalent water column height in
the atmosphere.  The simulation of the clear sky radiation was performed by the well
established radiation transfer model Libradtran [@Emde2016], a similar
approach, was also used by @Vamvakas2020 for creating a clear sky reference.

@@

<!-- Lookup table -->
To create a look up table that aligns with our dataset, we applied some adjustments.
To account for the Sun's variability in our one-minute GHI measurements, we corrected
the model's input spectrum integral, to the one of the total solar irradiance (TSI)
provided by NOAA [@Coddington2005].  Also, we applied the effect of the Earth -- Sun
distance on the irradiance, by using the distance calculated by the Astropy
[@AstropyCollaboration2022] software library. As needed, we interpolate the resulting
irradiances to the exact SZA of our measurements.  For each period of the year, we
used the appropriate atmospheric profile (afglms or afglmw).  Finally, we calculated
the clear sky irradiance value at the horizontal plane.  Thus, we were able to
emulate different atmospheric condition and levels of atmospheric clearness for the
climatological conditions of the site.  With this method, the modeled clear sky
irradiances can be directly compared to each measured one-minute value of GHI, for
different conditions of atmospheric clearness.

@@

.......here.....
